---
title: "Post-cop trait on paternity"
author: "Erin Macartney"
date: '2023-01-10'
output: html_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
message = FALSE,
warning = FALSE,
cache = TRUE, 
tidy = TRUE, 
echo = TRUE
)

rm(list = ls())
```

# Setting up {.tabset}

## Loading packages
```{r, message = FALSE}

# devtools::install_github('Mikata-Project/ggthemr', force = TRUE)

pacman::p_load(tidyverse, 
               here, 
               metafor, 
               clubSandwich, 
               orchaRd,
               rotl,
               ape,
               phytools,
               ggplot2,
               ggsignif,
               ggtree,
               ggthemr,
               ggtreeExtra,
               ggalluvial,
               clubSandwich)
```

## Loading data and functions
```{r, message = FALSE}
# dat <- read_csv(here("Data", "Data_raw.csv")) #raw data was used for data processing below

dat <- read_csv(here("Data", "processed_data.csv"))
source(here("R/func.R")) #functions for converting other statistics into correlations
tree <- read.tree(file = "species_tree.tre") #loading phylogenetic tree
```

## Calculating r

Note that this code runs on Data_raw.csv not Data_processed.csv
```{r, eval = FALSE}
effect_size_group2 <- with(dat, mapply(group2, 
                                       mean_low, mean_high, 
                                       SD_low, SD_high, 
                                       n_low, n_high))


#only selecting study that reported mean of for groups

# dat_a <- dat %>%
#   filter(First_author == "Yamane")

# effect_size_group4 <- with(dat_a, mapply(group4, 
#                                        mean_low, mean_med1, mean_med2, mean_high,
#                                        SD_low, SD_med1, SD_med2, SD_high,
#                                        n_low, n_med1, n_med2, n_high,
#                                        sim = 100000))

#manually added these correlations based on the function above


effect_size_est <- with(dat, mapply(est_se_b, estimate,SE, N))

effect_size_t <- with(dat, mapply(t_vals_b, t, N))

effect_size_F <- with(dat, mapply(F_vals_b, F, N, reverse = FALSE))

effect_size_p <- with(dat, mapply(p_vals_b, p, N, reverse = FALSE))


dat2 <- bind_cols(dat, "effect_size_group2" = effect_size_group2, "effect_size_est" =  effect_size_est, "effect_size_t" =  effect_size_t, "effect_size_F" = effect_size_F, "effect_size_p" = effect_size_p)

#removing unclear F stat direction
df2 <- subset(dat2, Effectsize_ID !='3')

#combining all r into one column

df3 <- df2 %>%
    select("Effectsize_ID","Corr_r", "effect_size_group2", "effect_size_est","effect_size_t", "effect_size_F", "effect_size_p")%>% pivot_longer(cols = -Effectsize_ID, values_to = "effect_size", names_to = "summary_statistic") %>% drop_na() 

#merging back with df2

df4 <- merge(df3, df2, by = "Effectsize_ID")

# df2 %>% pivot_longer(cols = c("Corr_r", "effect_size_group2", "effect_size_est","effect_size_t", "effect_size_F", "effect_size_p"), values_to = "effect_size", names_to = "summary_statistic") %>% drop_na(effect_size)

#flipping effect size so that higher = better
df4$effect_size2<- ifelse(df4$Coin == 2, -df4$effect_size, df4$effect_size) 

# write.csv(df4, "processed_data.csv")

```

## Making species tree

```{r, eval = FALSE}

length(unique(df4$Species)) #34 species
unique(df4$Species)

taxa <- tnrs_match_names(unique(df4$Species))
table(taxa$approximate_match) #34

# mytree <- tol_induced_subtree(ott_ids = taxa$ott_id, label_format= "name")
#HTTP failure: 400 [/v3/tree_of_life/induced_subtree] Error: node_id 'ott3411771' was not found!list(ott3411771 = "pruned_ott_id")

taxa[taxa[["ott_id"]] == "3411771", ] #gryllus_bimaculatus 
df4$Species[df4$Species == "Gryllus_bimaculatus"]  <- "Gryllus_bimaculata"
df4$Species[df4$Species == "Xiphophorus_helleri"]  <- "Xiphophorus_hellerii"

taxa <- tnrs_match_names(unique(df4$Species))

mytree <- tol_induced_subtree(ott_ids = taxa$ott_id, label_format= "name") # comes up with warning about dropping singleton nodes

sort(setdiff(unique(df4$Species), as.character(mytree$tip.label))) #"Drosophila_melanogaster" "Gadus_morhua"            "Gryllus_bimaculata"      "Sus_domestica" "Coregonus_lavaretus"  "Cyprinus_carpio"  names not matching
#allocating drosophila melanogaster to wrong ottID
#changing names of other species

# plot(mytree, show.tip.label = T, cex = 0.8, no.margin = TRUE)

#allocating correct OTTID
inspect(taxa, taxon_name = "Drosophila_melanogaster")
taxa <- update(taxa, taxon_name = "Drosophila_melanogaster", new_row_number = 1)

inspect(taxa, taxon_name = "Cyprinus_carpio")
taxa <- update(taxa, taxon_name = "Cyprinus_carpio", new_row_number = 1)

inspect(taxa, taxon_name = "Coregonus_lavaretus")
taxa <- update(taxa, taxon_name = "Coregonus_lavaretus", new_row_number = 1)

mytree <- tol_induced_subtree(ott_ids = taxa$ott_id, label_format= "name")

df4$Species[df4$Species == "Gryllus_bimaculata"]  <- "Gryllus_bimaculatus"
# mytree <- tol_induced_subtree(ott_ids = taxa$ott_id, label_format= "name")

# changing tip labels
mytree$tip.label[mytree$tip.label == "Sus_scrofa_domesticus"]  <- "Sus_domestica"
mytree$tip.label[mytree$tip.label == "Gadus_morhua_(species_in_domain_Eukaryota)"]  <- "Gadus_morhua"

sort(setdiff(unique(df4$Species), as.character(mytree$tip.label))) # all names match

plot(mytree, show.tip.label = T, cex = 0.8, no.margin = TRUE)
str(mytree)

write.tree(mytree, file = "species_tree.tre")
```

## Calculating Zr and Variance

```{r, eval = FALSE}


df4$N2 <- ifelse(df4$N_dependent == "dependent", df4$N, df4$N/2)


zr <- escalc(measure = "ZCOR", ni = df4$N2, ri = df4$effect_size2)

#adding back to dataframe 

df5 <- bind_cols(df4, zr)

write.csv(df5, "processed_data.csv")

```


# Data exploration {.tabset}

## Sample sizes

```{r}
#number of effect sizes

length(unique(dat$Effectsize_ID)) #note that effect_size2 has the effect size flipped so that higher = better
#why does data go down to 106 then?

#number of studies

length(unique(dat$Study_ID))

# Publication year range

min(dat$Year_published)
max(dat$Year_published)

#number of species
length(unique(dat$Species))

#number of classes
length(unique(dat$Class))

#number of classes
dat %>%
  group_by(Class) %>%
  summarise(n = n_distinct(Study_ID))

#traits
dat %>%
  group_by(PC_type) %>%
  summarise(n = n_distinct(Effectsize_ID))

# Cause of PC variation 

dat %>%
  group_by(PC_variation_cause) %>%
  summarise(n = n_distinct(Effectsize_ID))

# rearing type

dat %>%
  group_by(Rearing_type) %>%
  summarise(n = n_distinct(Study_ID))
```

## Alluvial plots

### Rearing type, Variation cause (For supplementary material)

```{r}
freq <- as.data.frame(table(dat$Rearing_type, dat$PC_variation_cause, dat$PC_type)) %>%
  rename("Raring_type" = Var1, "PC_variation_cause" = Var2)

# is_alluvia_form(as.data.frame(freq), axes = 1:2, silent = TRUE)

levels(freq$Raring_type) <- list("wild" = "1", "wild caught" = "2", "agri/aquiculure" = "3", "lab" = "4", "zoo" = "5", "other/unclear" = "6")

levels(freq$PC_variation_cause) <- list("natural" = "1", "plasticity" = "2","age" = "3", "direct manipulation" = "4", "selection" = "5", "other/unclear" = "6")

p <- ggplot(data = freq, aes(axis1 = Raring_type, axis2 = PC_variation_cause, y = Freq)) +
    geom_alluvium(aes(fill = Raring_type)) + geom_flow() + geom_stratum(aes(fill = Raring_type)) +
    geom_text(stat = "stratum", aes(label = after_stat(stratum))) + #theme_minimal() + geom_text(stat
    geom_text(stat = "stratum", aes(label = after_stat(stratum))) + #theme_minimal() + =
    geom_text(stat = "stratum", aes(label = after_stat(stratum))) + #theme_minimal() + "stratum",
    geom_text(stat = "stratum", aes(label = after_stat(stratum))) + #theme_minimal() + aes(label
    geom_text(stat = "stratum", aes(label = after_stat(stratum))) + #theme_minimal() + =
    geom_text(stat = "stratum", aes(label = after_stat(stratum))) + #theme_minimal() + after_stat(stratum)))
    geom_text(stat = "stratum", aes(label = after_stat(stratum))) + #theme_minimal() + +
    geom_text(stat = "stratum", aes(label = after_stat(stratum))) + #theme_minimal() + #theme_minimal()
    geom_text(stat = "stratum", aes(label = after_stat(stratum))) + #theme_minimal() + +
theme_void() + theme(legend.position = "none", plot.title = element_text(hjust = 0,
    vjust = 3), axis.title.x = element_text(), axis.text.x = element_text(face = "bold"),
    plot.margin = unit(c(1, 1, 0, 1), "cm")) + scale_x_discrete(limits = c("Raring type", "Variation cause"), expand = c(0.15, 0.05), position = "top") 

p


```
### Traits, variation cause

```{r}

freq1 <- as.data.frame(table(dat$PC_type, dat$PC_variation_cause, dat$PC_type)) %>%
  rename("PC_type" = Var1, "PC_variation_cause" = Var2)

levels(freq1$PC_variation_cause) <- list("natural" = "1", "plasticity" = "2","age" = "3", "direct manipulation" = "4", "selection" = "5", "other/unclear" = "6")

levels(freq1$PC_type) <- list("sperm number" = "1","testis size" = "2", "sperm length" = "3", "sperm velocity" = "4", "sperm normality" = "5", "total ejaculate size" = "6", "seminal fluid quantity" = "7", "accessory gland size" = "8")

p1 <- ggplot(data = freq1, aes(axis1 = PC_variation_cause, axis2 = PC_type, y = Freq)) +
    geom_alluvium(aes(fill = PC_variation_cause)) + geom_flow() + geom_stratum(aes(fill = PC_variation_cause)) +
    geom_text(stat = "stratum", aes(label = after_stat(stratum))) + #theme_minimal() + geom_text(stat
    geom_text(stat = "stratum", aes(label = after_stat(stratum))) + #theme_minimal() + =
    geom_text(stat = "stratum", aes(label = after_stat(stratum))) + #theme_minimal() + "stratum",
    geom_text(stat = "stratum", aes(label = after_stat(stratum))) + #theme_minimal() + aes(label
    geom_text(stat = "stratum", aes(label = after_stat(stratum))) + #theme_minimal() + =
    geom_text(stat = "stratum", aes(label = after_stat(stratum))) + #theme_minimal() + after_stat(stratum)))
    geom_text(stat = "stratum", aes(label = after_stat(stratum))) + #theme_minimal() + +
    geom_text(stat = "stratum", aes(label = after_stat(stratum))) + #theme_minimal() + #theme_minimal()
    geom_text(stat = "stratum", aes(label = after_stat(stratum))) + #theme_minimal() + +
theme_void() + theme(legend.position = "none", plot.title = element_text(hjust = 0,
    vjust = 3), axis.title.x = element_text(), axis.text.x = element_text(face = "bold"),
    plot.margin = unit(c(1, 1, 0, 1), "cm")) + scale_x_discrete(limits = c("Variation cause", "Trait"), expand = c(0.15, 0.05), position = "top") 

p1

```

### Fertilisation mode, competition order

```{r}

freq <- as.data.frame(table(dat$Fertilisation_mode, dat$Competition_order)) %>%
  rename("Fertilisation_mode" = Var1, "Competition_order" = Var2)

# is_alluvia_form(as.data.frame(freq), axes = 1:2, silent = TRUE)

levels(freq$Fertilisation_mode) <- list("internal" = "1", "external" = "2")

levels(freq$Competition_order) <- list("P1" = "1", "P2" = "2","Random mixing" = "3", "mating order controlled for" = "4")


p <- ggplot(data = freq, aes(axis1 = Fertilisation_mode, axis2 = Competition_order, y = Freq)) +
    geom_alluvium(aes(fill = Fertilisation_mode)) + geom_flow() + geom_stratum(aes(fill = Fertilisation_mode)) +
    geom_text(stat = "stratum", aes(label = after_stat(stratum))) + #theme_minimal() + geom_text(stat
    geom_text(stat = "stratum", aes(label = after_stat(stratum))) + #theme_minimal() + =
    geom_text(stat = "stratum", aes(label = after_stat(stratum))) + #theme_minimal() + "stratum",
    geom_text(stat = "stratum", aes(label = after_stat(stratum))) + #theme_minimal() + aes(label
    geom_text(stat = "stratum", aes(label = after_stat(stratum))) + #theme_minimal() + =
    geom_text(stat = "stratum", aes(label = after_stat(stratum))) + #theme_minimal() + after_stat(stratum)))
    geom_text(stat = "stratum", aes(label = after_stat(stratum))) + #theme_minimal() + +
    geom_text(stat = "stratum", aes(label = after_stat(stratum))) + #theme_minimal() + #theme_minimal()
    geom_text(stat = "stratum", aes(label = after_stat(stratum))) + #theme_minimal() + +
theme_void() + theme(legend.position = "none", plot.title = element_text(hjust = 0,
    vjust = 3), axis.title.x = element_text(), axis.text.x = element_text(face = "bold"),
    plot.margin = unit(c(1, 1, 0, 1), "cm")) + scale_x_discrete(limits = c("Fertilisation mode", "Competition order"), expand = c(0.15, 0.05), position = "top") 

p
```

### Traits, fertilisation mode

```{r}

freq2 <- as.data.frame(table(dat$Fertilisation_mode, dat$PC_type)) %>%
  rename("Fertilisation_mode" = Var1, "Trait" = Var2)

# is_alluvia_form(as.data.frame(freq), axes = 1:2, silent = TRUE)

levels(freq2$Fertilisation_mode) <- list("internal" = "1", "external" = "2")

levels(freq2$Trait) <- list("sperm number" = "1","testis size" = "2", "sperm length" = "3", "sperm velocity" = "4", "sperm normality" = "5", "total ejaculate size" = "6", "seminal fluid quantity" = "7", "accessory gland size" = "8")


p2 <- ggplot(data = freq2, aes(axis1 = Fertilisation_mode, axis2 = Trait, y = Freq)) +
    geom_alluvium(aes(fill = Fertilisation_mode)) + geom_flow() + geom_stratum(aes(fill = Fertilisation_mode)) +
    geom_text(stat = "stratum", aes(label = after_stat(stratum))) + #theme_minimal() + geom_text(stat
    geom_text(stat = "stratum", aes(label = after_stat(stratum))) + #theme_minimal() + =
    geom_text(stat = "stratum", aes(label = after_stat(stratum))) + #theme_minimal() + "stratum",
    geom_text(stat = "stratum", aes(label = after_stat(stratum))) + #theme_minimal() + aes(label
    geom_text(stat = "stratum", aes(label = after_stat(stratum))) + #theme_minimal() + =
    geom_text(stat = "stratum", aes(label = after_stat(stratum))) + #theme_minimal() + after_stat(stratum)))
    geom_text(stat = "stratum", aes(label = after_stat(stratum))) + #theme_minimal() + +
    geom_text(stat = "stratum", aes(label = after_stat(stratum))) + #theme_minimal() + #theme_minimal()
    geom_text(stat = "stratum", aes(label = after_stat(stratum))) + #theme_minimal() + +
theme_void() + theme(legend.position = "none", plot.title = element_text(hjust = 0,
    vjust = 3), axis.title.x = element_text(), axis.text.x = element_text(face = "bold"),
    plot.margin = unit(c(1, 1, 0, 1), "cm")) + scale_x_discrete(limits = c("Fertilisation mode", "Trait"), expand = c(0.15, 0.05), position = "top") 

p2
```

## Figure of species and class

```{r}
sample_data <- count(dat, Species)
sample_data <- as.data.frame(sample_data)
sample_data2 <- mutate(sample_data, tip.label = Species)

tree$tip.label <- strip_ott_ids(tree$tip.label, remove_underscores = TRUE)

sample_data3 <- left_join(sample_data2, dat[, c("Species", "Class")],
    by = "Species")

sample_data4 <- distinct(sample_data3, Species, .keep_all = TRUE)

sample_data4$tip.label <- gsub('_',' ',sample_data4$tip.label)

sample_data4$Species <- as.factor(sample_data4$Species)
sample_data4$tip.label <- as.factor(sample_data4$tip.label)
sample_data4$Class <- as.factor(sample_data4$Class)


#TODO Can't get this figure to work

tree2 <- ggtree(tree)
tree3 <- tree2 %<+% sample_data4 + geom_tippoint(aes(color = Class))+ scale_colour_manual(values = c("red", "green", "blue", "black", "yellow", "orange", "darkgreen"))


```

# Analysis {.tabset}

## Global effect size

```{r}

dat$Species[dat$Species == "Gryllus_bimaculata"]  <- "Gryllus_bimaculatus"

dat$Species[dat$Species == "Xiphophorus_helleri"]  <- "Xiphophorus_hellerii"

dat$Phylogeny <- gsub('_',' ',dat$Species)
tree$tip.label<- gsub('_',' ',tree$tip.label)



sort(setdiff(unique(dat$Phylogeny), as.character(tree$tip.label))) 
```

```{r, eval = FALSE}
branchlength<- compute.brlen(tree, method="Grafen", power=1)
VCV_species <- vcv(branchlength, corr=TRUE)


VCV <- impute_covariance_matrix(vi = dat$vi, cluster = dat$Study_ID, r = 0.5)


m0 <- rma.mv(yi = yi, V = VCV, 
             random = list(~1|Study_ID,
                          ~1|Effectsize_ID,
                          ~1|Species,
                         ~1|Phylogeny),
             R=list(Phylogeny = VCV_species),
             data = dat)

summary(m0)

round(i2_ml(m0), 2) #both species and phylo = 0% variation

# m0b <- rma.mv(yi = yi, V = VCV, random = list(~1|Study_ID,
#                                             ~1|Effectsize_ID),
#                                             #~1|Species,
#                                             #~1|Phylogeny),
#              #R=list(Phylogeny = VCV_species),
#              data = dat)
# 
# summary(m0b)
# 
# anova(m0b, m0) # reduced model as slightly lower ARC (delta = 4)


```

```{r}
orchard_plot(m0, mod = "1", xlab = "zr", alpha=0.4, group = "Study_ID", data = dat) 
 
```

## Meta-regression {.tabset}

### Traits

```{r}

#removing trait 2 (testes size)
# 
dat1 <- subset(dat, PC_type !=2)

dat1$PC_type<-as.factor(dat1$PC_type)

VCV1 <- impute_covariance_matrix(vi = dat1$vi, cluster = dat1$Study_ID, r = 0.5)

levels(dat1$PC_type) <- list("sperm number" = "1", "sperm length" = "3", "sperm velocity" = "4", "sperm normality" = "5", "total ejaculate size" = "6", "seminal fluid quantity" = "7", "accessory gland size" = "8")
                    

m1 <- rma.mv(yi = yi, V = VCV1, mod = ~PC_type-1,  
             random = list(~1|Study_ID,
                          ~1|Effectsize_ID,
                          ~1|Species,
                         ~1|Phylogeny),
             R=list(Phylogeny = VCV_species),
             test = "t",
             data = dat1)


summary(m1)

r2_ml(m1)


fig.2 <- orchard_plot(m1, mod = "PC_type", group = "Study_ID", data = dat1, xlab = "zr", alpha=0.4) +
  theme(axis.text.y = element_text(angle = 45))

fig.2

```

### Trait variation cause

```{r}

dat$PC_variation_cause<-as.factor(dat$PC_variation_cause)

levels(dat$PC_variation_cause) <- list("natural" = "1", "environmental plasticity" = "2", "age" = "3", "direct manipulation" = "4", "experimental selection" = "5", "other" = "6")

#TODO should we remove 'other'?


m2 <- rma.mv(yi = yi, V = VCV, mod = ~PC_variation_cause-1,  
             random = list(~1|Study_ID,
                          ~1|Effectsize_ID,
                          ~1|Species,
                         ~1|Phylogeny),
             R=list(Phylogeny = VCV_species),
             test = "t",
             data = dat)

summary(m2)

r2_ml(m2)


fig.3 <- orchard_plot(m2, mod = "PC_variation_cause", group = "Study_ID", data = dat, xlab = "zr", alpha=0.4) +
  theme(axis.text.y = element_text(angle = 45))

fig.3

```

### Lab vs Wild-caught

```{r}

#removing 3 (agriculture)

dat2 <- subset(dat, Rearing_type !=3)

dat2$Rearing_type<-as.factor(dat2$Rearing_type)

VCV2 <- impute_covariance_matrix(vi = dat2$vi, cluster = dat2$Study_ID, r = 0.5)

levels(dat2$Rearing_type) <- list("wild" = "1", "wild caught" = "2", "lab" = "4", "other/unclear" = "6")


m3 <- rma.mv(yi = yi, V = VCV2, mod = ~Rearing_type-1,  
             random = list(~1|Study_ID,
                          ~1|Effectsize_ID,
                          ~1|Species,
                         ~1|Phylogeny),
             R=list(Phylogeny = VCV_species),
             test = "t",
             data = dat2)

summary(m3)

r2_ml(m3)

#TODO should we remove other/unclear? I think so

fig.4 <- orchard_plot(m3, mod = "Rearing_type", group = "Study_ID", data = dat2, xlab = "zr", alpha=0.4) +
  theme(axis.text.y = element_text(angle = 45))

fig.4

```

### Internal vs external fertilisation



```{r}

dat$Fertilisation_mode<-as.factor(dat$Fertilisation_mode)

levels(dat$Fertilisation_mode) <- list("internal" = "1", "external" = "2")

m4 <- rma.mv(yi = yi, V = VCV, mod = ~Fertilisation_mode-1,  
             random = list(~1|Study_ID,
                          ~1|Effectsize_ID,
                          ~1|Species,
                         ~1|Phylogeny),
             R=list(Phylogeny = VCV_species),
             test = "t",
             data = dat)

summary(m4)

r2_ml(m4)


fig.5 <- orchard_plot(m4, mod = "Fertilisation_mode", group = "Study_ID", data = dat, xlab = "zr", alpha=0.4)+
  theme(axis.text.y = element_text(angle = 45)) 

fig.5 #no difference between fertilisation mode but lets looks at subanalysis. Perhaps different traits are doing different things.

```

#### Combined fert mode and trait


```{r}

dat$Fert_trait <- paste(dat$Fertilisation_mode, dat$PC_type, sep = " ")

m4c <- rma.mv(yi = yi, V = VCV, mod = ~Fert_trait-1,  
             random = list(~1|Study_ID,
                          ~1|Effectsize_ID,
                          ~1|Species,
                         ~1|Phylogeny),
             R=list(Phylogeny = VCV_species),
             test = "t",
             data = dat)

summary(m4c)

fig.5c <- orchard_plot(m4c, mod = "Fert_trait", group = "Study_ID", data = dat, xlab = "zr", alpha=0.4)+
  theme(axis.text.y = element_text(angle = 45)) 

fig.5c
```

#### Internal sub-analysis

```{r}

dat3 <- subset(dat, Fertilisation_mode == "internal")

dat3 <- subset(dat3, PC_type !=2)

VCV3 <- impute_covariance_matrix(vi = dat3$vi, cluster = dat3$Study_ID, r = 0.5)


dat3$PC_type<-as.factor(dat3$PC_type)


levels(dat3$PC_type) <- list("sperm number" = "1", "sperm length" = "3", "sperm velocity" = "4", "sperm normality" = "5", "total ejaculate size" = "6", "seminal fluid quantity" = "7", "accessory gland size" = "8")


m4a <- rma.mv(yi = yi, V = VCV3, mod = ~PC_type-1,  
              random = list(~1|Study_ID,
                          ~1|Effectsize_ID,
                          ~1|Species,
                         ~1|Phylogeny),
             R=list(Phylogeny = VCV_species),
             test = "t",
             data = dat3)

summary(m4a)
r2_ml(m4a)


fig.5a <- orchard_plot(m4a, mod = "PC_type", group = "Study_ID", data = dat3, xlab = "zr", alpha=0.4)+
  theme(axis.text.y = element_text(angle = 45)) 

fig.5a

```

#### External sub-analysis

```{r}
dat4 <- subset(dat, Fertilisation_mode == "external")

dat4 <- subset(dat4, PC_type !=2)

VCV4 <- impute_covariance_matrix(vi = dat4$vi, cluster = dat4$Study_ID, r = 0.5)


dat4$PC_type<-as.factor(dat4$PC_type)

levels(dat4$PC_type) <- list("sperm number" = "1", "sperm length" = "3", "sperm velocity" = "4", "sperm normality" = "5", "total ejaculate size" = "6", "seminal fluid quantity" = "7", "accessory gland size" = "8")


m4b <- rma.mv(yi = yi, V = VCV4, mod = ~PC_type-1,  
              random = list(~1|Study_ID,
                          ~1|Effectsize_ID,
                          ~1|Species,
                         ~1|Phylogeny),
             R=list(Phylogeny = VCV_species),
             test = "t",
             data = dat4)

summary(m4b)
r2_ml(m4b)


fig.5b <- orchard_plot(m4b, mod = "PC_type", group = "Study_ID", data = dat4, xlab = "zr", alpha=0.4)+
  theme(axis.text.y = element_text(angle = 45)) 

fig.5b

```

```{r}
fig.5c <- (fig.5a + fig.5b)http://127.0.0.1:38297/graphics/plot_zoom_png?width=1200&height=900
fig.5c #no differences in traits between internal and external fertilisers
```

### Precedence 

```{r}
#TODO need to think about this category some more
#TODO could also do subanalysis
#TODO Not sure how to deal with this category. Might be too hard

dat$Precendence<-as.factor(dat$Precendence)

m5 <- rma.mv(yi = yi, V = vi, mod = ~Precendence-1,  
             random = list(~1|Study_ID,
                          ~1|Effectsize_ID,
                          ~1|Species,
                         ~1|Phylogeny),
             R=list(Phylogeny = VCV_species),
             test = "t",
             data = dat)

summary(m5)

r2_ml(m5)


fig.6 <- orchard_plot(m5, mod = "Precendence", group = "Study_ID", data = dat, xlab = "zr", alpha=0.4) 

fig.6
```

7### Competition order 

```{r}
#TODO a sub analysis for this might make more sense and test for differences in traits and phylo signal

dat$Competition_order<-as.factor(dat$Competition_order)


levels(dat$Competition_order) <- list("P1" = "1", "P2" = "2", "Random mixing" = "3", "mating order controlled for" = "4")

m6 <- rma.mv(yi = yi, V = VCV, mod = ~Competition_order-1,  
             random = list(~1|Study_ID,
                          ~1|Effectsize_ID,
                          ~1|Species,
                         ~1|Phylogeny),
             R=list(Phylogeny = VCV_species),
             test = "t",
             data = dat)

summary(m6)

r2_ml(m6)


m6b <- rma.mv(yi = yi, V = vi, mod = ~Competition_order,  
             random = list(~1|Study_ID,
                          ~1|Effectsize_ID,
                          ~1|Species,
                         ~1|Phylogeny),
             R=list(Phylogeny = VCV_species),
             test = "t",
             data = dat)

summary(m6b)


fig.7 <- orchard_plot(m6, mod = "Competition_order", group = "Study_ID", data = dat, xlab = "zr", alpha=0.4) +
  theme(axis.text.y = element_text(angle = 45)) 

fig.7
```

#### P1 and P2 sub-analysis

```{r}
#have grouped p1 and p2 because both are assumed to be loaded raffles. 

dat5 <- subset(dat, Competition_order  %in% c("P1", "P2"))

dat5$PC_type<-as.factor(dat5$PC_type)

VCV5 <- impute_covariance_matrix(vi = dat5$vi, cluster = dat5$Study_ID, r = 0.5)


levels(dat5$PC_type) <- list("sperm number" = "1", "sperm length" = "3", "sperm velocity" = "4", "sperm normality" = "5", "total ejaculate size" = "6", "seminal fluid quantity" = "7", "accessory gland size" = "8")


m6a <- rma.mv(yi = yi, V = VCV5, mod = ~PC_type-1,  
              random = list(~1|Study_ID,
                          ~1|Effectsize_ID,
                          ~1|Species,
                         ~1|Phylogeny),
             R=list(Phylogeny = VCV_species),
             test = "t",
             data = dat5)

summary(m6a)
r2_ml(m6a)


fig.7a <- orchard_plot(m6a, mod = "PC_type", group = "Study_ID", data = dat5, xlab = "zr", alpha=0.4)+
  theme(axis.text.y = element_text(angle = 45)) 

#TODO need to remove normality, and velocity
```

#### Random mixing sub-analysis

```{r}

dat6 <- subset(dat, Competition_order == "Random mixing")

dat6$PC_type<-as.factor(dat6$PC_type)

VCV6 <- impute_covariance_matrix(vi = dat6$vi, cluster = dat6$Study_ID, r = 0.5)


levels(dat6$PC_type) <- list("sperm number" = "1", "sperm length" = "3", "sperm velocity" = "4", "sperm normality" = "5", "total ejaculate size" = "6", "seminal fluid quantity" = "7", "accessory gland size" = "8")


m6b <- rma.mv(yi = yi, V = VCV6, mod = ~PC_type-1,  
              random = list(~1|Study_ID,
                          ~1|Effectsize_ID,
                          ~1|Species,
                         ~1|Phylogeny),
             R=list(Phylogeny = VCV_species),
             test = "t",
             data = dat6)

summary(m6b)
r2_ml(m6b)


fig.7b <- orchard_plot(m6b, mod = "PC_type", group = "Study_ID", data = dat6, xlab = "zr", alpha=0.4)+
  theme(axis.text.y = element_text(angle = 45)) 

```


```{r}
fig.7c <- (fig.7a + fig.7b)
fig.7c 

#TODO could instead do sub analyses within traits
```

## Publication bias and sensitvity analysis