---
title: "Ejaculate traits and paternity share under sperm competition: a meta-analysis across species and fertilisation modes"
author: Erin L Macartney, Kyle Morrison, Rhonda R Snook, Malgorzata Lagisz, Shinichi
  Nakagawa
output: 
    rmdformats::readthedown:
      code_folding: hide
      code_download: true
      toc_depth: 4
editor_options: 
  chunk_output_type: consolet
---

```{r, include = FALSE}
knitr::opts_chunk$set(
message = FALSE,
warning = FALSE,
cache = TRUE, 
tidy = TRUE, 
echo = TRUE
)

rm(list = ls())
```

# Setting up {.tabset}

## Loading packages
```{r, message = FALSE}

# devtools::install_github('Mikata-Project/ggthemr', force = TRUE)

# if (!require("BiocManager", quietly = TRUE))
# install.packages("BiocManager")
# 
# BiocManager::install(version = '3.16')
# BiocManager::install("ggtree", force = TRUE)

pacman::p_load(dplyr,
               tidyr,
               readr,
               here, 
               metafor, 
               clubSandwich, 
               orchaRd,
               rotl,
               ape,
               tibble,
               phytools,
               ggplot2,
               ggsignif,
               ggtree,
               ggthemr,
               ggtreeExtra,
               ggalluvial,
               patchwork,
               clubSandwich,
               MuMIn)


eval(metafor:::.MuMIn)
```

## Loading data and functions
Loading processed data (need to unhash for raw data), phylogenetic tree, and custom functions to convert discrete groups, test statistics etc to correlations.

```{r, message = FALSE}
#Code for loading raw data
#dat <- read_csv(here("Data", "Data_raw.csv")) #raw data was used for data processing below

dat <- read_csv(here("Data", "processed_data.csv"))
source(here("R/func.R")) #functions for converting other statistics into correlations
tree <- read.tree(here("R", "species_tree.tre")) #loading phylogenetic tree
```

## Calculating r

Note that this code runs on Data_raw.csv not Data_processed.csv
```{r, eval = FALSE}
effect_size_group2 <- with(dat, mapply(group2, 
                                       mean_low, mean_high, 
                                       SD_low, SD_high, 
                                       n_low, n_high))


effect_size_est <- with(dat, mapply(est_se_b, estimate,SE, N))

effect_size_t <- with(dat, mapply(t_vals_b, t, N))

effect_size_F <- with(dat, mapply(F_vals_b, F, N, reverse = FALSE))

effect_size_p <- with(dat, mapply(p_vals_b, p, N, reverse = FALSE))


dat2 <- bind_cols(dat, "effect_size_group2" = effect_size_group2, 
                      "effect_size_est" =  effect_size_est, 
                      "effect_size_t" =  effect_size_t, 
                      "effect_size_F" = effect_size_F, 
                      "effect_size_p" = effect_size_p)

#removing unclear F stat direction
df2 <- subset(dat2, Effectsize_ID !='3')

#combining all r into one column

df3 <- df2 %>%
    select("Effectsize_ID","Corr_r", "effect_size_group2", 
    "effect_size_est","effect_size_t", "effect_size_F", "effect_size_p") %>% 
    pivot_longer(cols = -Effectsize_ID, values_to = "effect_size", names_to = "summary_statistic") %>% 
    drop_na() 

#merging back with df2

df4 <- merge(df3, df2, by = "Effectsize_ID")

#flipping effect size so that higher = better
df4$effect_size2<- ifelse(df4$Coin == 2, -df4$effect_size, df4$effect_size) 

```

## Making species tree
```{r, eval = FALSE}

length(unique(df4$Species)) #34 species
unique(df4$Species)

taxa <- tnrs_match_names(unique(df4$Species))
# table(taxa$approximate_match) #34

taxa[taxa[["ott_id"]] == "3411771", ] #gryllus_bimaculatus 
df4$Species[df4$Species == "Gryllus_bimaculatus"]  <- "Gryllus_bimaculata"
df4$Species[df4$Species == "Xiphophorus_helleri"]  <- "Xiphophorus_hellerii"

taxa <- tnrs_match_names(unique(df4$Species))

mytree <- tol_induced_subtree(ott_ids = taxa$ott_id, label_format= "name") # comes up with warning about dropping singleton nodes

# sort(setdiff(unique(df4$Species), as.character(mytree$tip.label)))
#"Drosophila_melanogaster" "Gadus_morhua"            "Gryllus_bimaculata"      "Sus_domestica" "Coregonus_lavaretus"  "Cyprinus_carpio"  names not matching
#allocating drosophila melanogaster to wrong ottID

#changing names of other species

#allocating correct OTTID
inspect(taxa, taxon_name = "Drosophila_melanogaster")
taxa <- update(taxa, taxon_name = "Drosophila_melanogaster", new_row_number = 1)

inspect(taxa, taxon_name = "Cyprinus_carpio")
taxa <- update(taxa, taxon_name = "Cyprinus_carpio", new_row_number = 1)

inspect(taxa, taxon_name = "Coregonus_lavaretus")
taxa <- update(taxa, taxon_name = "Coregonus_lavaretus", new_row_number = 1)

mytree <- tol_induced_subtree(ott_ids = taxa$ott_id, label_format= "name")

df4$Species[df4$Species == "Gryllus_bimaculata"]  <- "Gryllus_bimaculatus"
# mytree <- tol_induced_subtree(ott_ids = taxa$ott_id, label_format= "name")

# changing tip labels
mytree$tip.label[mytree$tip.label == "Sus_scrofa_domesticus"]  <- "Sus_domestica"
mytree$tip.label[mytree$tip.label == "Gadus_morhua_(species_in_domain_Eukaryota)"]  <- "Gadus_morhua"
mytree$tip.label[mytree$tip.label == "Luciobarbus_capito"] <- "Cyprinus_carpio"

sort(setdiff(unique(df4$Species), as.character(mytree$tip.label))) # all names match

plot(mytree, show.tip.label = T, cex = 0.8, no.margin = TRUE)
# str(mytree)

write.tree(mytree, file = "species_tree.tre")
```

## Calculating Zr and Variance
```{r, eval = FALSE}

df4$N2 <- ifelse(df4$N_dependent == "dependent", df4$N/2, df4$N)

df5 <- escalc(measure = "ZCOR", ni = df4$N2, ri = df4$effect_size2, data = df4)

#adding back to dataframe 
#df5 <- bind_cols(df4, zr)

write.csv(df5, "processed_data.csv")
```

# Data exploration {.tabset}

## Sample sizes
```{r, eval = FALSE}
# number of effect sizes
length(unique(dat$Effectsize_ID)) #note that effect_size2 has the effect size flipped so that higher = better

#number of studies
length(unique(dat$Study_ID))

# number of animal groups
length(unique(dat$Group_ID))

# Publication year range
min(dat$Year_published)
max(dat$Year_published)

#number of species
length(unique(dat$Species))

#number of classes
length(unique(dat$Class))

#number of classes
dat %>%
  group_by(Class) %>%
  summarise(n = n_distinct(Study_ID))

#fertilisation mode
dat %>%
  group_by(Fertilisation_mode) %>%
  summarise(n = n_distinct(Effectsize_ID))

#traits
dat %>%
  group_by(PC_type) %>%
  summarise(n = n_distinct(Effectsize_ID))

# Cause of PC variation 
dat %>%
  group_by(PC_variation_cause2) %>%
  summarise(n = n_distinct(Effectsize_ID))

#focal male_internal fertilisation
dat_int <- subset(dat, Fertilisation_mode == 1)

dat_int %>%
  group_by(Competition_order) %>%
  summarise(n = n_distinct(Effectsize_ID))

```

# Analysis {.tabset}

## Global effect size
```{r}

dat$Species[dat$Species == "Gryllus_bimaculata"]  <- "Gryllus_bimaculatus"

dat$Phylogeny <- gsub('_',' ',dat$Species)
tree$tip.label<- gsub('_',' ',tree$tip.label)

# sort(setdiff(unique(dat$Phylogeny), as.character(tree$tip.label))) 
```

```{r}
branchlength<- compute.brlen(tree, method="Grafen", power=1)
VCV_species <- vcv(branchlength, corr=TRUE)


VCV <- impute_covariance_matrix(vi = dat$vi, cluster = dat$Study_ID, r = 0.5)


m0 <- rma.mv(yi = yi, V = VCV, 
             random = list(~1|Study_ID,
                          ~1|Effectsize_ID,
                          ~1|Species,
                         ~1|Phylogeny),
             R=list(Phylogeny = VCV_species),
             data = dat)

summary(m0, transfm = "tanh") 
round(i2_ml(m0), 2) 

```

## Meta-regression {.tabset}

### Post-copulatory trait type
```{r, message = FALSE}

#removing trait 2 (testes size)

dat1 <- subset(dat, PC_type !=2)

dat1$PC_type<-as.factor(dat1$PC_type)

VCV1 <- impute_covariance_matrix(vi = dat1$vi, cluster = dat1$Study_ID, r = 0.5)

levels(dat1$PC_type) <- list("sperm number" = "1", "sperm length" = "3", "sperm velocity" = "4", "sperm normality" = "5", "total ejaculate size" = "6", "seminal fluid quantity" = "7")
                    

m1 <- rma.mv(yi = yi, V = VCV1, mod = ~PC_type-1,  
             random = list(~1|Study_ID,
                          ~1|Effectsize_ID,
                          ~1|Species,
                         ~1|Phylogeny),
             R=list(Phylogeny = VCV_species),
             test = "t",
             data = dat1)


summary(m1)

r2_ml(m1)

res1 <- mod_results(m1, mod = "PC_type", data = dat1, group = "Study_ID")

fig.3a <- orchard_plot(res1 , mod = "PC_type", group = "Study_ID", xlab = "Correlation (r)", alpha=0.4, transfm = "tanh") +
  theme(axis.text.y = element_text(angle = 45)) +
   scale_colour_manual(values = c("grey34","grey34","grey34","grey34","grey34","grey34")) +
  scale_fill_manual(values=c("grey34","grey34","grey34","grey34","grey34","grey34"))  + geom_signif(comparisons = list(c("Seminal fluid quantity", "Total ejaculate size", "Sperm normality", "Sperm velocity", "Sperm length", "Sperm number")),
              annotations = "*")

fig.3a

```

### Fertilisation mode
```{r, message = FALSE}

dat$Fertilisation_mode<-as.factor(dat$Fertilisation_mode)

levels(dat$Fertilisation_mode) <- list("internal" = "1", "external" = "2")

m2 <- rma.mv(yi = yi, V = VCV, mod = ~Fertilisation_mode-1,  
             random = list(~1|Study_ID,
                          ~1|Effectsize_ID,
                          ~1|Species,
                         ~1|Phylogeny),
             R=list(Phylogeny = VCV_species),
             test = "t",
             data = dat)

summary(m2)

r2_ml(m2)

m2b <- rma.mv(yi = yi, V = VCV, mod = ~Fertilisation_mode,  
             random = list(~1|Study_ID,
                          ~1|Effectsize_ID,
                          ~1|Species,
                         ~1|Phylogeny),
             R=list(Phylogeny = VCV_species),
             test = "t",
             data = dat)

summary(m2b) # not signficantly different - TODO (need to get all the contrasts? - Erin)

res2 <- mod_results(m2, mod = "Fertilisation_mode", data = dat, group = "Study_ID")

fig.3b <- orchard_plot(res2, mod = "Fertilisation_mode", group = "Study_ID", xlab = "Correlation (r)", alpha=0.4, transfm = "tanh")+
  ylim(-1,1.25) +
  scale_colour_manual(values = c("grey34","grey34")) +
  scale_fill_manual(values=c("grey34","grey34"))  +
  theme(axis.text.y = element_text(angle = 45))+
    geom_signif(comparisons = list(c("Internal", "External")),
              annotations = "*")

fig.3b 

```

### Trait variation cause
```{r, message = FALSE}

dat2 <- subset(dat, PC_variation_cause2 !=6)

dat2$PC_variation_cause2<-as.factor(dat2$PC_variation_cause2)

levels(dat2$PC_variation_cause2) <- list("genetic + environmental" = "1", "environmental plasticity" = "2", "age" = "3", "direct manipulation" = "4", "genetic variation" = "5")

VCV2 <- impute_covariance_matrix(vi = dat2$vi, cluster = dat2$Study_ID, r = 0.5)

m3 <- rma.mv(yi = yi, V = VCV2, mod = ~PC_variation_cause2-1,  
             random = list(~1|Study_ID,
                          ~1|Effectsize_ID,
                          ~1|Species,
                         ~1|Phylogeny),
             R=list(Phylogeny = VCV_species),
             test = "t",
             data = dat2)

summary(m3)

r2_ml(m3)


res3 <- mod_results(m3, mod = "PC_variation_cause2", data = dat2, group = "Study_ID")

fig.3c <- orchard_plot(res3, mod = "PC_variation_cause2", group = "Study_ID", xlab = "Correlation (r)", alpha=0.4, transfm = "tanh") +
  theme(axis.text.y = element_text(angle = 45)) +
  scale_colour_manual(values = c("grey34","grey34", "grey34","grey34", "grey34","grey34")) +
  scale_fill_manual(values=c("grey34","grey34", "grey34","grey34", "grey34","grey34"))  +
  theme(axis.text.y = element_text(angle = 45)) +
    geom_signif(comparisons = list(c("Other", "Experimental selection", "Direct manipulation", "Age", "Environmental plasticity", "Natural")),
              annotations = "*")

fig.3c
```

## Sub-analyses {.tabset}

### Sperm number

#### Global model
```{r,}

dat3 <- subset(dat, PC_type == 1)
dat3$Species <- as.factor(dat3$Species)

# dat3 %>%
#   group_by(Species) %>%
#   summarise(n = n_distinct(Effectsize_ID))

# dat3 %>%
#   group_by(Species) %>%
#   summarise(n = n_distinct(Study_ID))

VCV3 <- impute_covariance_matrix(vi = dat3$vi, cluster = dat3$Study_ID, r = 0.5)

m4 <- rma.mv(yi = yi, V = VCV3, 
             random = list(~1|Study_ID,
                          ~1|Effectsize_ID,
                          ~1|Species,
                         ~1|Phylogeny),
             R=list(Phylogeny = VCV_species),
             data = dat3)

# summary(m4, transfm = "tanh")

round(i2_ml(m4), 2)
```

#### Fertilisation mode meta-regression
```{r,}
m4_MR <- rma.mv(yi = yi, V = VCV3, mod = ~Fertilisation_mode-1,  
              random = list(~1|Study_ID,
                          ~1|Effectsize_ID,
                          ~1|Species,
                         ~1|Phylogeny),
             R=list(Phylogeny = VCV_species),
             test = "t",
             data = dat3)

summary(m4_MR)
r2_ml(m4_MR)

res4 <- mod_results(m4_MR, mod = "Fertilisation_mode", data = dat3, group = "Study_ID")

fig.4a <- orchard_plot(res4, mod = "Fertilisation_mode", group = "Study_ID", xlab = "Correlation (r)", alpha=0.4, transfm = "tanh")+ ylim(-1,1.25) +
  theme(axis.text.y = element_text(angle = 45)) +
  ggtitle('Sperm number') +
    geom_signif(comparisons = list(c("internal", "external")),
              annotations = "*")

fig.4a
```

### Sperm length

#### Global model
```{r,}
dat4 <- subset(dat, PC_type == 3)

# dat4 %>%
#   group_by(Species) %>%
#   summarise(n = n_distinct(Effectsize_ID))
# dat4 %>%
#   group_by(Species) %>%
#   summarise(n = n_distinct(Study_ID))

VCV4 <- impute_covariance_matrix(vi = dat4$vi, cluster = dat4$Study_ID, r = 0.5)

m5 <- rma.mv(yi = yi, V = VCV4, 
             random = list(~1|Study_ID,
                          ~1|Effectsize_ID,
                          ~1|Species,
                         ~1|Phylogeny),
             R=list(Phylogeny = VCV_species),
             data = dat4)

# summary(m5, transfm = "tanh")

round(i2_ml(m5), 2) 
```

#### Fertilisation mode meta-regression

```{r,}
m5_MR <- rma.mv(yi = yi, V = VCV4, mod = ~Fertilisation_mode-1,  
              random = list(~1|Study_ID,
                          ~1|Effectsize_ID,
                          ~1|Species,
                         ~1|Phylogeny),
             R=list(Phylogeny = VCV_species),
             test = "t",
             data = dat4)

summary(m5_MR)
r2_ml(m5_MR)

res5 <- mod_results(m5_MR, mod = "Fertilisation_mode", data = dat4, group = "Study_ID")

fig.4b <- orchard_plot(res5, mod = "Fertilisation_mode", group = "Study_ID", xlab = "Correlation (r)", alpha=0.4, transfm = "tanh")+ ylim(-1,1.25) +
  theme(axis.text.y = element_text(angle = 45)) +
  ggtitle("Sperm length") +
    geom_signif(comparisons = list(c("internal", "external")),
              annotations = "*")

fig.4b
```

### Sperm velocity

#### Global model
```{r}
dat5<- subset(dat, PC_type == 4)

# dat5 %>%
#   group_by(Species) %>%
#   summarise(n = n_distinct(Effectsize_ID))
# 
# dat5 %>%
#   group_by(Species) %>%
#   summarise(n = n_distinct(Study_ID))

VCV5 <- impute_covariance_matrix(vi = dat5$vi, cluster = dat5$Study_ID, r = 0.5)

m6 <- rma.mv(yi = yi, V = VCV5, 
             random = list(~1|Study_ID,
                          ~1|Effectsize_ID,
                          ~1|Species,
                         ~1|Phylogeny),
             R=list(Phylogeny = VCV_species),
             data = dat5)

# summary(m6, transfm = "tanh")

round(i2_ml(m6), 2)
```

#### Fertilisation mode meta-regression
```{r,}
m6_MR <- rma.mv(yi = yi, V = VCV5, mod = ~Fertilisation_mode-1,  
              random = list(~1|Study_ID,
                          ~1|Effectsize_ID,
                          ~1|Species,
                         ~1|Phylogeny),
             R=list(Phylogeny = VCV_species),
             test = "t",
             data = dat5)

summary(m6_MR)
r2_ml(m6_MR)

res5 <- mod_results(m6_MR, mod = "Fertilisation_mode", data = dat5, group = "Study_ID")

fig.4c <- orchard_plot(res5, mod = "Fertilisation_mode", group = "Study_ID", xlab = "Correlation (r)", alpha=0.4, transfm = "tanh")+ ylim(-1,1.25) +
  theme(axis.text.y = element_text(angle = 45))+
  ggtitle("Sperm velocity") +
    geom_signif(comparisons = list(c("internal", "external")),
              annotations = "*")

fig.4c
```

## Publication bias and sensitivity analysis {.tabset}

### Multi-moderator model
```{r}
dat_fm <- subset(dat, PC_type !=2)

VCV_fm <- impute_covariance_matrix(vi = dat_fm$vi, cluster = dat_fm$Study_ID, r = 0.5)

mod_fm <- rma.mv(yi = yi, V = VCV_fm, mod = ~PC_type-1 + Fertilisation_mode-1 + PC_variation_cause2-1,  
             random = list(~1|Study_ID,
                          ~1|Effectsize_ID,
                          ~1|Species,
                         ~1|Phylogeny),
             R=list(Phylogeny = VCV_species),
             test = "t",
             data = dat_fm)
# 
# summary(mod_fm)
# 
# r2_ml(mod_fm)

res_fm <- dredge(mod_fm, trace = 2)

res_fm2 <- subset(res_fm, delta <= 4, recalc.weights = FALSE)
sw(res_fm2)
```

### Funnel plots
```{r}

# funnel plot
# funnel(m0, xlab = "Zr", ylab = "Standard Eror")

# funnel plot on full model 
funnel(mod_fm, xlab = "Zr", ylab = "Standard Eror", yaxis = "seinv")


```

### Small-study effects 
```{r}

# small study effect
dat$sei <- sqrt(dat$vi)
egger <- rma.mv(yi = yi, V = VCV, 
             mod = ~sei,
             random = list(~1|Study_ID,
                          ~1|Effectsize_ID,
                          ~1|Species,
                         ~1|Phylogeny),
             R=list(Phylogeny = VCV_species),
             data = dat)

# no statistical evidence for small-study effect
summary(egger)

```

### Decline effect
```{r}

# decline effect
dat$cYear <- scale(dat$Year_published, center = TRUE, scale = FALSE)

#model doesn't converge with variance VCV so have to use vi
decline <- rma.mv(yi = yi, V = vi, 
             mod = ~cYear,
             random = list(~1|Study_ID,
                          ~1|Effectsize_ID,
                          ~1|Species,
                         ~1|Phylogeny),
             R=list(Phylogeny = VCV_species),
             data = dat)

# no statistical evidence for decline effect
summary(decline)
```

### Leave-one-group-out
```{r}

dat <- dat %>%
    mutate(leave_out = paste(First_author, Year_published, sep = "_"))
dat$leave_out <- as.factor(dat$leave_out)
dat$Year_published <- as.integer(dat$Year_published)

dat$Study_ID <- as.factor(dat$Study_ID)

LeaveOneOut_effectsize <- list()
for (i in 1:length(levels(dat$leave_out))) {
    d <- dat %>%
        filter(leave_out != levels(dat$leave_out)[i])

    VCV_leaveout <- impute_covariance_matrix(vi = d$vi, cluster = d$Study_ID, r = 0.5)

    LeaveOneOut_effectsize[[i]] <- rma.mv(yi = yi, V = VCV_leaveout, random = list(~1 |
        Study_ID, ~1 | Effectsize_ID, ~1| Species), method = "REML", data = d[d$leave_out !=
        levels(d$leave_out)[i], ])
}

# writing function for extracting est, ci.lb, and ci.ub from all models
est.func <- function(model) {
    df <- data.frame(est = model$b, lower = model$ci.lb, upper = model$ci.ub)
    return(df)
}

# using dplyr to form data frame
MA_oneout <- lapply(LeaveOneOut_effectsize,function(x) est.func(x)) %>%
    bind_rows %>%
    mutate(left_out = levels(dat$leave_out))


```

```{r}

# telling ggplot to stop reordering factors
MA_oneout$left_out <- as.factor(MA_oneout$left_out)
MA_oneout$left_out <- factor(MA_oneout$left_out, levels = MA_oneout$left_out)

# plotting
leaveoneout <- ggplot(MA_oneout) + geom_hline(yintercept = 0, lty = 2, lwd = 1) +
    geom_hline(yintercept = m0$ci.lb, lty = 3, lwd = 0.75, colour = "black") +
    geom_hline(yintercept = m0$b, lty = 1, lwd = 0.75, colour = "black") + geom_hline(yintercept = m0$ci.ub,
    lty = 3, lwd = 0.75, colour = "black") + geom_pointrange(aes(x = left_out, y = est,
    ymin = lower, ymax = upper)) + xlab("Study left out") + ylab("Zr, 95% CI") +
    coord_flip() + theme(panel.grid.minor = element_blank()) + theme_bw() + theme(panel.grid.major = element_blank()) +
    theme(panel.grid.minor.x = element_blank()) + theme(axis.text.y = element_text(size = 6))

leaveoneout

```

### Analysing total sperm length only {.tabset}

#### Global model
```{r, message = FALSE, warning=FALSE}
#reducing the dataframe so that only the effect sizes of total sperm length are included
dat$PC_type_notes <- as.factor(dat$PC_type_notes)

dat_SLtotal <- subset(dat, !(PC_type_notes %in% c("tail", "head", "midpiece")))

VCV <- impute_covariance_matrix(vi = dat_SLtotal$vi, cluster = dat_SLtotal$Study_ID, r = 0.5)

m0a <- rma.mv(yi = yi, V = VCV, 
             random = list(~1|Study_ID,
                          ~1|Effectsize_ID,
                          ~1|Species,
                         ~1|Phylogeny),
             R=list(Phylogeny = VCV_species),
             data = dat_SLtotal)

summary(m0a, transfm = "tanh") 

round(i2_ml(m0a), 2) 
```

#### Post-copulatory trait type
```{r}
dat_SLtotala<- subset(dat_SLtotal, PC_type !=2)
dat_SLtotala <- subset(dat_SLtotala, PC_type !=8)

dat_SLtotala$PC_type<-as.factor(dat_SLtotala$PC_type)

VCV1a <- impute_covariance_matrix(vi = dat_SLtotala$vi, cluster = dat_SLtotala$Study_ID, r = 0.5)

levels(dat_SLtotala$PC_type) <- list("sperm number" = "1", "sperm length" = "3", "sperm velocity" = "4", "sperm normality" = "5", "total ejaculate size" = "6", "seminal fluid quantity" = "7")
#                     

m1a <- rma.mv(yi = yi, V = VCV1a, mod = ~PC_type-1,  
             random = list(~1|Study_ID,
                          ~1|Effectsize_ID,
                          ~1|Species,
                         ~1|Phylogeny),
             R=list(Phylogeny = VCV_species),
             test = "t",
             data = dat_SLtotala)

summary(m1a)

r2_ml(m1a)
```

#### Fertilisation mode
```{r}
dat_SLtotal$Fertilisation_mode<-as.factor(dat_SLtotal$Fertilisation_mode)

levels(dat_SLtotal$Fertilisation_mode) <- list("internal" = "1", "external" = "2")

m2a <- rma.mv(yi = yi, V = VCV, mod = ~Fertilisation_mode-1,  
             random = list(~1|Study_ID,
                          ~1|Effectsize_ID,
                          ~1|Species,
                         ~1|Phylogeny),
             R=list(Phylogeny = VCV_species),
             test = "t",
             data = dat_SLtotal)

summary(m2a)

r2_ml(m2a)

```

#### Sperm length sub-analysis
```{r}
dat6 <- subset(dat_SLtotal, PC_type == 3)

VCV6c <- impute_covariance_matrix(vi = dat6$vi, cluster = dat6$Study_ID, r = 0.5)

m6c <- rma.mv(yi = yi, V = VCV6c, 
             random = list(~1|Study_ID,
                          ~1|Effectsize_ID,
                          ~1|Species,
                         ~1|Phylogeny),
             R=list(Phylogeny = VCV_species),
             data = dat6)
# 
# summary(m6c, transfm = "tanh")

round(i2_ml(m6c), 2) 

m6_MRc <- rma.mv(yi = yi, V = VCV6c, mod = ~Fertilisation_mode-1,  
              random = list(~1|Study_ID,
                          ~1|Effectsize_ID,
                          ~1|Species,
                         ~1|Phylogeny),
             R=list(Phylogeny = VCV_species),
             test = "t",
             data = dat6)

summary(m6_MRc)
r2_ml(m6_MRc)

```

# Figures {.tabset}

## Fig.1
Note that this was mostly edited outside of R
```{r}
#TODO not sure why this code has stopped working?

sample_data <- count(dat, Species)
sample_data <- as.data.frame(sample_data)
sample_data2 <- mutate(sample_data, tip.label = Species)

# tree$tip.label <- strip_ott_ids(tree$tip.label, remove_underscores = TRUE)

sample_data3 <- left_join(sample_data2, dat[, c("Species", "Class")],
    by = "Species")

sample_data4 <- distinct(sample_data3, Species, .keep_all = TRUE)

sample_data4$tip.label <- gsub('_',' ',sample_data4$tip.label)

sample_data4$Species <- as.character(sample_data4$Species)
sample_data4$tip.label <- as.character(sample_data4$tip.label)
sample_data4$Class <- as.factor(sample_data4$Class)

#prepare effect sizes counts data
# sample_data4$Species <- sub('Xiphophorus_helleri','Xiphophorus_hellerii', sample_data4$Species) #fix typo
data_species_count_K <- sample_data4$n
names(data_species_count_K) <- sample_data4$Species #add row names

#prepare papers counts data
papers_counts <- dat %>% group_by(Species) %>% summarize(distinct_papers = n_distinct(Paper_ID)) %>% deframe() #using library(tibble)

data_papers_count_N_tree <- papers_counts[match(tree$tip.label, names(papers_counts))]  # reorder counts to match the order of tips 

#prepare Class data
sample_data4$Class <- as.factor(sample_data4$Class)
#levels(sample_data4$Class)

#set colors (by Class) for the plot
color_bgroup <- c("#00A1D5", "#999933", "#A20056", "#E9AF1D", "#E18727", "#661100", "#117733")[sample_data4$Class] #assign colors to Class - based on levels(data_species_bgroup) #biological groups - https://r-charts.com/color-palettes/
names(color_bgroup) <- sample_data4$Species #make it a named vector
color_bgroup_tip <- color_bgroup[match(tree$tip.label, names(color_bgroup))]  # reorder colors to match the order of tips on the tree
data_species_count_K_tree <- data_species_count_K[match(tree$tip.label, names(data_species_count_K))]  # reorder counts to match the order of tips on the tree

#plot locally using base graphics
plot.new()
plot(tree, x.lim = 100, y.lim = length(sample_data4$Species)+2, cex = 1, tip.color = color_bgroup_tip, label.offset = 1, edge.color = "grey", font = 3)
phydataplot(data_species_count_K, tree, col = color_bgroup_tip, offset = 40, scaling = 2, border = "white", lwd = 3, legend = "side") #add counts of effect sizes bars 
text(90, length(sample_data4$Species)+2, "effect sizes (papers)", font=3) #add counts label
text(95, 1:length(data_species_count_K_tree), data_species_count_K_tree) #add counts of effect sizes numbers 
text(100, 1:length(data_papers_count_N_tree), paste("(", data_papers_count_N_tree, ")")) #add counts of effect sizes numbers 

```

## Fig.2 
```{r}
res0 <- mod_results(m0, mod = "1", data = dat, group = "Study_ID")

Fig.2 <- orchard_plot(res0, mod = "1", xlab = "Correlation (r)", 
                    group = "Study_ID", alpha=0.4, transfm = "tanh") +
  scale_colour_manual(values = c("grey34")) +
  scale_fill_manual(values=c("grey34")) 

  # geom_errorbarh(data = res0, aes(xmin = lowerPR, xmax = upperPR), 
  #     height = 0, show.legend = FALSE, size = 1.1, alpha = 0.5) +
  # geom_errorbarh(aes(xmin = lowerCL, xmax = upperCL), 
  #     height = 0.05, show.legend = FALSE, size = 2)　+
  # geom_point(aes(fill = name), shape = 21)+
  # scale_size_continuous(range = c(1, 7))+
  # theme(panel.border = element_rect(colour = "black", fill=NA))

# #TODO previous code to modify oarchard plot no longer works
Fig.2
```


## Fig.3
```{r,}

Fig.3 <- (fig.3a/fig.3b/fig.3c)+ plot_annotation(tag_levels = 'A')

Fig.3
```

## Fig.4
```{r}

Fig.4 <- (fig.4a / fig.4b/fig.4c) + plot_annotation(tag_levels = 'A')
Fig.4

```

## Fig.5
```{r}
funnel(mod_fm, xlab = "Zr", ylab = "Standard Eror", yaxis = "seinv")
```

## Fig.S3
```{r}

freq1 <- as.data.frame(table(dat$Fertilisation_mode, dat$PC_type, dat$PC_variation_cause2)) %>%
  rename("Fertilisation_mode" = Var1, "Trait" = Var2, "Variation_cause" = Var3)

levels(freq1$Fertilisation_mode) <- list("internal" = "1", "external" = "2")

levels(freq1$Trait) <- list("sperm number" = "1","testis size" = "2", "sperm length" = "3", "sperm velocity" = "4", "sperm normality" = "5", "total ejaculate size" = "6", "seminal fluid quantity" = "7", "accessory gland size" = "8")

levels(freq1$Variation_cause) <- list("genetic + environment" = "1", "environmental plasticity" = "2", "age" = "3", "direct manipulation" = "4", "artificial selcetion" = "5", "unclear/other" = "6")

FigS3 <- ggplot(data = freq1, aes(axis1 = Fertilisation_mode, axis2 = Trait, axis3 = Variation_cause, y = Freq)) +
    geom_alluvium(aes(fill = Fertilisation_mode)) + geom_flow() + geom_stratum(aes(fill = Fertilisation_mode)) +
    geom_text(stat = "stratum", aes(label = after_stat(stratum))) + #theme_minimal() + geom_text(stat
    geom_text(stat = "stratum", aes(label = after_stat(stratum))) + #theme_minimal() + +
theme_void() + theme(legend.position = "none", plot.title = element_text(hjust = 0,
    vjust = 3), axis.title.x = element_text(), axis.text.x = element_text(face = "bold"),
    plot.margin = unit(c(1, 1, 0, 1), "cm")) + scale_x_discrete(limits = c("Fertilisation mode", "Postcopulatory trait", "Variation cause"), expand = c(0.15, 0.05), position = "top") 
```

## Fig.S4
```{r}
res0 <- mod_results(m0a, mod = "1", data = dat_SLtotal, group = "Study_ID")

FigS4 <- orchard_plot(res0, mod = "1", xlab = "Correlation (r)", 
                    group = "Study_ID", alpha=0.4, transfm = "tanh") +
  scale_colour_manual(values = c("grey34")) +
  scale_fill_manual(values=c("grey34")) 

FigS4
```

## Fig.S5
```{r, message=FALSE}
res1a <- mod_results(m1a, mod = "PC_type", data = dat_SLtotala, group = "Study_ID")

figS5a <- orchard_plot(res1a , mod = "PC_type", group = "Study_ID", data = dat_SLtotala, xlab = "Correlation (r)", alpha=0.4, transfm = "tanh") +
  theme(axis.text.y = element_text(angle = 45)) +
  ggtitle('Post-copulatory trait as a moderator in global model') +
    geom_signif(comparisons = list(c("Seminal fluid quantity", "Total ejaculate size", "Sperm normality", "Sperm velocity", "Sperm length", "Sperm number")),
              annotations = "*")

res2a <- mod_results(m2a, mod = "Fertilisation_mode", data = dat_SLtotal, group = "Study_ID")

figS5b <- orchard_plot(res2a, mod = "Fertilisation_mode", group = "Study_ID", data = dat_SLtotal, xlab = "Correlation (r)", alpha=0.4, transfm = "tanh")+
  scale_colour_manual(values = c("grey34","grey34")) +
  scale_fill_manual(values=c("grey34","grey34"))  +
  theme(axis.text.y = element_text(angle = 45)) +
  ggtitle('Fertilisation mode as a moderator in global model') +
    geom_signif(comparisons = list(c("Internal", "External")),
              annotations = "*")

res3a <- mod_results(m6_MRc, mod = "Fertilisation_mode", data = dat6, group = "Study_ID")

figS5c <- orchard_plot(res3a, mod = "Fertilisation_mode", group = "Study_ID", data = dat6, xlab = "Correlation (r)", alpha=0.4, transfm = "tanh")+ ylim(-1,1.25) +
  theme(axis.text.y = element_text(angle = 45)) +
  ggtitle('Sperm length sub-analysis')

Fig.S5 <- (figS5a/figS5b/figS5c) + plot_annotation(tag_levels = 'A')
Fig.S5
```

## Fig.S6
Note that most of this figure was manually edited outside of R
``` {r, eval = FALSE}
#creating tree of species that only had sperm length
length(unique(dat4$Species)) #12 species
dat4$Species <-as.character(dat4$Species)

taxa <- tnrs_match_names(unique(dat4$Species))

taxa[taxa[["ott_id"]] == "3411771", ] #gryllus_bimaculatus 
dat4$Species[dat4$Species == "Gryllus_bimaculatus"]  <- "Gryllus_bimaculata"
dat4$Species[dat4$Species == "Xiphophorus_helleri"]  <- "Xiphophorus_hellerii"

taxa <- tnrs_match_names(unique(dat4$Species))

mytree <- tol_induced_subtree(ott_ids = taxa$ott_id, label_format= "name")

#allocating correct OTTID
inspect(taxa, taxon_name = "Drosophila_melanogaster")
taxa <- update(taxa, taxon_name = "Drosophila_melanogaster", new_row_number = 1)

mytree_spermlength <- tol_induced_subtree(ott_ids = taxa$ott_id, label_format= "name")

dat4$Species[dat4$Species == "Gryllus_bimaculata"]  <- "Gryllus_bimaculatus"

# changing tip labels
mytree_spermlength$tip.label[mytree_spermlength$tip.label == "Sus_scrofa_domesticus"]  <- "Sus_domestica"
mytree_spermlength$tip.label[mytree_spermlength$tip.label == "Gadus_morhua_(species_in_domain_Eukaryota)"]  <- "Gadus_morhua"
mytree_spermlength$tip.label[mytree_spermlength$tip.label == "Luciobarbus_capito"] <- "Cyprinus_carpio"

sort(setdiff(unique(dat4$Species), as.character(mytree_spermlength$tip.label))) # all names match

plot(mytree_spermlength, show.tip.label = T, cex = 0.8, no.margin = TRUE)
# str(mytree)

write.tree(mytree_spermlength, file = "mytree_spermlength.tre")
```

```{r, eval = FALSE}
mytree_spermlength <- read.tree(here("R", "mytree_spermlength.tre"))

plottree <- ggtree(mytree_spermlength) + 
  geom_tiplab(size = 3, hjust = -0.1, align = TRUE)

# plot(plottree)
dat4$Species <- as.factor(dat4$Species)

#Taking the average effect size per species
dat4_averageeffect <- dat4 %>%
  group_by(Species) %>%
  summarize(mean_zr = mean(yi))

Figs6 <- facet_plot(plottree, panel="dot", data=dat4_averageeffect, geom=geom_point, aes(x=mean_zr), size=2.5) +
  theme(axis.title.x=element_text(size=10),
        axis.text.x=element_text(size=10)) +
  geom_vline(xintercept=0) 

Figs6

```

## Fig.S7
Note that most of this figure was manually edited outside of R
```{r, eval = FALSE}
#creating tree of species that only had sperm velocity
length(unique(dat5$Species)) #13 species
dat5$Species <-as.character(dat5$Species)

taxa <- tnrs_match_names(unique(dat5$Species))

taxa[taxa[["ott_id"]] == "3411771", ] #gryllus_bimaculatus 
dat5$Species[dat5$Species == "Gryllus_bimaculatus"]  <- "Gryllus_bimaculata"
dat5$Species[dat5$Species == "Xiphophorus_helleri"]  <- "Xiphophorus_hellerii"

taxa <- tnrs_match_names(unique(dat5$Species))

mytree <- tol_induced_subtree(ott_ids = taxa$ott_id, label_format= "name")

#allocating correct OTTID
inspect(taxa, taxon_name = "Coregonus_lavaretus")
taxa <- update(taxa, taxon_name = "Coregonus_lavaretus", new_row_number = 1)

mytree_spermvelocity <- tol_induced_subtree(ott_ids = taxa$ott_id, label_format= "name")

dat5$Species[dat5$Species == "Gryllus_bimaculata"]  <- "Gryllus_bimaculatus"

# changing tip labels
mytree_spermvelocity$tip.label[mytree_spermvelocity$tip.label == "Sus_scrofa_domesticus"]  <- "Sus_domestica"
mytree_spermvelocity$tip.label[mytree_spermvelocity$tip.label == "Gadus_morhua_(species_in_domain_Eukaryota)"]  <- "Gadus_morhua"
mytree_spermvelocity$tip.label[mytree_spermvelocity$tip.label == "Luciobarbus_capito"] <- "Cyprinus_carpio"

sort(setdiff(unique(dat5$Species), as.character(mytree_spermvelocity$tip.label))) # all names match

plot(mytree_spermvelocity, show.tip.label = T, cex = 0.8, no.margin = TRUE)
# str(mytree)

write.tree(mytree_spermvelocity, file = "mytree_spermvelocity.tre")
```

```{r}

mytree_spermvelocity <- read.tree(here("R", "mytree_spermvelocity.tre"))

plottree <- ggtree(mytree_spermvelocity) + 
  geom_tiplab(size = 3, hjust = -0.1, align = TRUE)

plot(plottree)
dat5$Species <- as.factor(dat5$Species)

#Taking the average effect size per species
dat5_averageeffect <- dat5 %>%
  group_by(Species) %>%
  summarize(mean_zr = mean(yi))

Figs7 <- facet_plot(plottree, panel="dot", data=dat5_averageeffect, geom=geom_point, aes(x=mean_zr), size=2.5) +
  theme(axis.title.x=element_text(size=10),
        axis.text.x=element_text(size=10)) +
  geom_vline(xintercept=0) 

Figs7

```

## Fig.S8
```{r,}

bubble_plot(egger, mod = "sei", group = "Study_ID", 
              xlab = "1/SE (N - 3)", ylab = "Effect size (Zr)", data = dat)
```

## Fig.S9
```{r,}
bubble_plot(decline, mod = "cYear", group = "Study_ID",
              xlab = "Centred (Publicaiton year)", ylab = "Effect size (Zr)",data = dat)
```

## Fig.S10
```{r,}
leaveoneout
```
